### 2016-11-02 ms/coverLetter/coverLetter.tex
added cover letter

  When a species goes extinct, more than a species is lost. That
  species interacted with other species in its community, likely in
  ways that were important or even crucial to others' survival. As the
  world continues to lose species at an alarming rate, it has become
  increasingly imperative to aid the recovery of lost interactions and
  component biodviersity through ecological restoration. We know
  little, however, about how to re-assemble interacting communities
  through restoration, or the process of ecological network assembly
  more generally.

  Using extensive surveys of pollinators spanning eight years
  comprising \texttildelow $20,000$ pollinator visitation records, we
  explore the assembly of plant-pollinator communities at native plant
  restorations in the Central Valley of California. Employing newly
  developed methods for exmaining the temporal changes in networks, we
  find that species are highly dynamic in their network position,
  causing community assembly to be punctuated by major interaction
  reorganizations. The most persistent and generalized species were
  also the most variable in their network positions, contrary to what
  is expected through prefereantial attachment theory --- an assembly
  theory otherwise well-supported in the network literature. Our study
  is the first long-term study on the temporal assembly of ecological
  networks.

@@

  Regards,
  Lauren C. Ponisio, PhD
  Claire Kremen, Professor

>>>>

  When a species goes extinct, more than a species is lost. That
  species interacted with other species in its community, likely in
  ways that were important or even crucial to others' survival. As the
  world continues to lose species at an alarming rate, it has become
  increasingly imperative to aid the recovery of lost interactions and
  component biodiversity through ecological restoration. We know
  little, however, about how to re-assemble interacting communities
  through restoration, or the process of ecological network assembly
  more generally.

  Using extensive surveys of pollinators spanning eight years
  comprising \texttildelow $20,000$ pollinator visitation records, we
  explore the assembly of plant-pollinator communities at native plant
  restorations in the Central Valley of California. Employing newly
  developed methods for examining temporal changes in networks, we
  find that species are highly dynamic in their network position,
  causing community assembly to be punctuated by major interaction
  reorganizations. The most persistent and generalized species were
  also the most variable in their network positions, contrary to what
  is expected through preferential attachment theory --- an assembly
  theory otherwise well-supported in the network literature. Our study
  is the first long-term study on the temporal assembly of ecological
  networks. It also challenges the hypothesis that mutualistic systems
  assemble through preferential attachment (Bascompte and Stouffer,
  2009).

@@

  Regards,
  Lauren C. Ponisio, PhD\\
  Claire Kremen, Professor

### 2016-11-02 ms/ms.tex
added cover letter

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 
  \item Main text word count: 
  \item Number of references: 
  \item Number of figures:
  \end{itemize}
}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turned
  over at higher rates in assembling hedgerows as the networks
  continually reorganized. Nestedness of assembling networks also
  increased through time, but there was no increase in robustness to
  simulated plant extinctions. The sensitivity of networks to
  cascading perturbations, however, increased as the communities
  assembled, at least partially due to accumulating species
  richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation provision in agricultural areas.
\end{abstract}

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations, such as the decrease in
abundance of a plant or pollinator, can have negative consequences for
the species in the network. For example, a decrease in abundance of a
pollinator will diminish the pollination services it provides to
plants. The affected plants would set less seeds, and decrease in
abundance the subsequent year. Consequently, other pollinators that
depended on those plant species would also be affected, and the
effects of this perturbation would continue to propagate throughout
the network. Alternatively, perturbations could also have a positive
effect. For example, the increase in abundance of a plant species
would lead to an increase in resource availability for the
pollinators. The examples of negative perturbations (e.g., resource
collapse, disease spreading, parasites), however, outnumber possible
positive perturbations. It is important to note that both robustness
and algebraic connectivity assume that the network is static. They do
not account for the ability of species to alter their interaction
depending on circumstances and the resource availability.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would expect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of monitoring
the assembly process or the drought is not possible. Interestingly,
most assembling hedgerows did not undergo a significant interaction
reorganization immediately after a hedgerow was planted (i.e., the
transition from weedy field margin to hedgerow). This result is
consistent with the finding that in our study system, hedgerow
restoration takes several years to have an impact on the
plant-pollinator communities, and with the observation that hedgerows
do not begin to produce many flowers until $3$--$5$ years following
planting (Kremen and M'Gonigle, in prep).

>>>>

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage[numbers]{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 148
  \item Main text word count: 5152
  \item Number of references: 65
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
  The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness.
% (Gaiarsa et al., in prep)
 Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations, such as the decrease in
abundance of a plant or pollinator, can have negative consequences for
the species in the network. For example, a decrease in abundance of a
pollinator will diminish the pollination services it provides to
plants. The affected plants would set less seeds, and decrease in
abundance the subsequent year. Consequently, other pollinators that
depended on those plant species would also be affected, and the
effects of this perturbation would continue to propagate throughout
the network. Alternatively, perturbations could also have a positive
effect. For example, the increase in abundance of a plant species
would lead to an increase in resource availability for the
pollinators. The examples of negative perturbations (e.g., resource
collapse, disease spreading, parasites), however, outnumber possible
positive perturbations. It is important to note that both robustness
and algebraic connectivity assume that the network is static. They do
not account for the ability of species to alter their interaction
depending on circumstances and the resource availability.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would expect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of monitoring
the assembly process or the drought is not possible. Interestingly,
most assembling hedgerows did not undergo a significant interaction
reorganization immediately after a hedgerow was planted (i.e., the
transition from weedy field margin to hedgerow). This result is
consistent with the finding that in our study system, hedgerow
restoration takes several years to have an impact on the
plant-pollinator communities, and with the observation that hedgerows
do not begin to produce many flowers until $3$--$5$ years following
planting \citep{kremen-2015-602}.
